---
title: "PCA"
author: "zxm"
date: 2017-07-02
categories: ["R"]
tags: ["PCA", "data visualization"]
---

## Applications of PCA

### Data Visualization

```{r, warning = F, message = F}
summary(iris)

# Customize the colors
setcols = c("#00AFBB", "#E7B800", "#FC4E07")

# Customize the lower panel: correlation efficients
correlation.panel = function(x, y){
  usr = par("usr"); on.exit(par(usr))
  par(usr = c(0, 1, 0, 1))
  
  # 3 types of correlation
  rp = round(cor(x, y, method = "pearson"), digits = 2)
  text(0.5, 0.75, paste("Pearson's r = ", rp))
  
  rs = round(cor(x, y, method = "spearman"), digits = 2)
  text(0.5, 0.5, bquote("Spearman's "~rho~" = "~.(rs)))
  
  rk = round(cor(x, y, method = "kendall"), digits = 2)
  text(0.5, 0.25, bquote("Kendall's "~tau~" = "~.(rk)))
}

# Customize upper panel: scatter plots
scatterplot.panel = function(x, y){
  points(x, y, pch = 16,
  col = setcols[iris$Species])
}

pairs(iris[1:4], 
      lower.panel = correlation.panel, 
      upper.panel = scatterplot.panel)
```


```{r, warning = F, message = F}
# install.packages("ggfortify")
library(ggfortify)
setcols = c("#00AFBB", "#E7B800", "#FC4E07")
autoplot(prcomp(iris[1:4]), colour = setcols[iris$Species])
```

**Reference**

1. [Scatter Plot Matrices - R Base Graphs](http://www.sthda.com/english/wiki/scatter-plot-matrices-r-base-graphs)
2. [Data visualization: Dimension Reduction - Principal Components Analysis](http://siret.ms.mff.cuni.cz/sites/default/files/doc/david.hoksza/lectures/vis/04-pca.pdf)
3. [Plotting PCA (Principal Component Analysis)](https://cran.r-project.org/web/packages/ggfortify/vignettes/plot_pca.html)
4. [5 functions to do Principal Components Analysis in R](http://gastonsanchez.com/visually-enforced/how-to/2012/06/17/PCA-in-R/)
5. [Principal component analysis in R : prcomp() vs. princomp() - R software and data mining](http://www.sthda.com/english/wiki/principal-component-analysis-in-r-prcomp-vs-princomp-r-software-and-data-mining)
6. [fviz_pca: Quick Principal Component Analysis data visualization - R software and data mining](http://www.sthda.com/english/wiki/fviz-pca-quick-principal-component-analysis-data-visualization-r-software-and-data-mining)
7. [Principal Component Analysis: How to reveal the most important variables in your data?](http://www.sthda.com/english/wiki/principal-component-analysis-how-to-reveal-the-most-important-variables-in-your-data-r-software-and-data-mining)